This is the sample article title\protect\thanks{This is an example for title footnote.}

### 2020-04-29 index.Rmd
changed graphics paths, updated index.Rmd

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{sim_sce=2}
\caption{One hundred noisy curves in the functional manifold of normal probability density.}
\label{fig:sce2}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{sim_sce=4}
\caption{One hundred noisy curves in the functional manifold of square root probability density functions.}
\label{fig:sce4}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{sim_sce=5}
\caption{One hundred noisy curves in the functional manifold of warped functions.}
\label{fig:sce5}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=0.3\textheight]{sim_results/sce=2_SNR=high_Kobs=30_MSE}
\includegraphics[height=0.3\textheight]{sim_results/sce=2_SNR=high_Kobs=30_isometry}
\includegraphics[height=0.3\textheight]{sim_results/sce=2_SNR=high_Kobs=30_Pearson}
\caption{Manifold of $N(\beta,1)$ probability density functions. The boxplots indicate the distributions of each of the three metrics over 100 Monte Carlo samples. Across all three metrics, our method with $s=2$ performs the best, followed by our method with $s=3$.}
\label{fig:normal}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=0.3\textheight]{sim_results/sce=5_SNR=high_Kobs=30_MSE}
\includegraphics[height=0.3\textheight]{sim_results/sce=5_SNR=high_Kobs=30_isometry}
\includegraphics[height=0.3\textheight]{sim_results/sce=5_SNR=high_Kobs=30_Pearson}
\caption{Manifold of warped functions. The boxplots indicate the distributions of each of the three metrics over 100 Monte Carlo samples. The best performing estimators are given by our method with $s=2$ and then $s=3$.}
\label{fig:warping}
\end{figure}

\begin{figure}
\includegraphics[height=0.3\textheight]{sim_results/sce=4_SNR=high_Kobs=30_MSE}
\includegraphics[height=0.3\textheight]{sim_results/sce=4_SNR=high_Kobs=30_isometry}
\includegraphics[height=0.3\textheight]{sim_results/sce=4_SNR=high_Kobs=30_Pearson}
\caption{Manifold of square root Beta densities. The boxplots indicate the distributions of each of the three metrics over 100 Monte Carlo samples. Besides Spline IsoGeo, all methods perform comparably well.}
\label{fig:betas}
\end{figure}

>>>>

# RELATED WORK

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{./graphics/sim_sce=2}
\includegraphics[width=0.3\textwidth]{./graphics/sim_sce=4}
\includegraphics[width=0.3\textwidth]{./graphics/sim_sce=5}
\caption{Left: One hundred noisy curves in the functional manifold of normal probability density. Middle: One hundred noisy curves in the functional manifold of square root probability density functions. Right: One hundred noisy curves in the functional manifold of warped functions.}
\label{fig:sce2} 
\end{figure}
<!-- previous labels {fig:sce4} and {fig:sce5} need to be updated -->

@@

@@

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{./graphics/sce=2_SNR=high_Kobs=30_MSE}
\includegraphics[width=0.3\textwidth]{./graphics/sce=2_SNR=high_Kobs=30_isometry}
\includegraphics[width=0.3\textwidth]{./graphics/sce=2_SNR=high_Kobs=30_Pearson}
\caption{Manifold of $N(\beta,1)$ probability density functions. The boxplots indicate the distributions of each of the three metrics over 100 Monte Carlo samples. Across all three metrics, our method with $s=2$ performs the best, followed by our method with $s=3$.}
\label{fig:normal}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{./graphics/sce=5_SNR=high_Kobs=30_MSE}
\includegraphics[width=0.3\textwidth]{./graphics/sce=5_SNR=high_Kobs=30_isometry}
\includegraphics[width=0.3\textwidth]{./graphics/sce=5_SNR=high_Kobs=30_Pearson}
\caption{Manifold of warped functions. The boxplots indicate the distributions of each of the three metrics over 100 Monte Carlo samples. The best performing estimators are given by our method with $s=2$ and then $s=3$.}
\label{fig:warping}
\end{figure}

\begin{figure}
\includegraphics[width=0.3\textwidth]{./graphics/sce=4_SNR=high_Kobs=30_MSE}
\includegraphics[width=0.3\textwidth]{./graphics/sce=4_SNR=high_Kobs=30_isometry}
\includegraphics[width=0.3\textwidth]{./graphics/sce=4_SNR=high_Kobs=30_Pearson}
\caption{Manifold of square root Beta densities. The boxplots indicate the distributions of each of the three metrics over 100 Monte Carlo samples. Besides Spline IsoGeo, all methods perform comparably well.}
\label{fig:betas}
\end{figure}

### 2020-04-29 writing/wrapper_sadm.tex
changed graphics paths, updated index.Rmd

\begin{biography}{\includegraphics[width=60pt,height=70pt,draft]{empty}}{\textbf{Author Name.} This is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text.}
\end{biography}

>>>>

\begin{biography}{\includegraphics[width=60pt,height=70pt,draft]{graphics/empty}}{\textbf{Author Name.} This is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text.}
\end{biography}
